---
title: "T Test Example"
author: "Dan Seefeldt"
date: "July 5, 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## T Test example with R

Here the goal is the answer the question: Is there a difference in means of male's and female's creditbalance limit?

data set curousy of: https://archive.ics.uci.edu/ml/datasets/default+of+credit+card+clients

First let's grab the two columns we need: SEX and LIMIT_BAL

```{r cars}
cc_data <- read.csv("default of credit card clients.csv")

gender_limit <- cc_data[,2:3]

gender_limit["SEX"][gender_limit["SEX"] == 1] <- "Male"
gender_limit["SEX"][gender_limit["SEX"] == 2] <- "Female"



```

Let's explore the data a little with some bar charts.

```{r, echo=FALSE}
counts <- table(gender_limit$SEX)

barplot(counts, main="Gender Distribution", xlab="Gender")


```

The data looks to be right skewed.


```{r, echo=FALSE}
counts <- table(gender_limit$LIMIT_BAL)

barplot(counts, main="Balance Limit Distribution", xlab="Balance Limit")


```

A box plot shows that as well.

```{r, echo=FALSE}


boxplot(LIMIT_BAL ~ SEX, data = gender_limit, xlab = "Gender",
   ylab = "Credit Limit", main = "Credit Limit Boxplot")

```

Normality Plot and normaility tests show this data is not a normal distribution. Takinghte log of the data does not change this fact. As this is an exersize in the general process of a T Test we will pretend it is and conduct the T Test.

```{r, echo=FALSE}


qqnorm(gender_limit$LIMIT_BAL, main = "balance")
qqline(gender_limit$LIMIT_BAL)

```


```{r, echo=FALSE}

shapiro_sample <- gender_limit[sample(nrow(gender_limit), 5000), ]

shapiro.test(shapiro_sample$LIMIT_BAL)

ks.test(gender_limit$LIMIT_BAL, 'pnorm')

```

Hypothesis test: 
H0: There is no differece of credit limit between males and females
h1: there is a difference of credit limit between males and females


```{r, echo=FALSE}


t.test(gender_limit$LIMIT_BAL ~ gender_limit$SEX)


```
